Tailwind Test Doc

### 2023-04-22 TailwindTest.qmd
testing tailwind cdn

---
title: "Tailwind Test Doc"
editor: visual
---

ssss

<script src="https://cdn.tailwindcss.com"></script>

sssss

xxxx

@@

@@

@@

![](images/image-1130704809.png)

>>>>

---
title: "Tailwind Test Doc"
editor: visual

format:
  html:
    css: styles.css

---
<!-- tailwind cdn temp link -->
<script src = "https://cdn.tailwindcss.com"></script>
<!---->

<div class="bg-gradient-to-r from-indigo-500 from-10% via-purple-500 via-30% to-pink-500 to-90% ...">
  <!-- ... -->
  xxxxxx
</div>

xxxxxx

<div class="bg-gradient-to-r from-indigo-500 from-10% via-purple-500 via-30% to-pink-500 to-90% ...">
  <!-- ... -->
  include content
</div>

@@

<p .bg-sky-900>

include content

</p>

@@

.bg-sky-900

@@
